Data preparation

### 2023-07-26 procesamiento/prod_analysis.Rmd
modelos ok

@@

```{r class-homclass}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot)
load(here::here("input/data/proc/study1.RData"))

df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (I+II)"
                                           ))

df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (II - lower grade)",
                                           "Service class (I - higher grade)" 
                                           ))
df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
                          as.factor = T,
                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
frq(df1$Q05pcm)
dfreg <- df1 %>% dplyr::select(redist,
                        class6,
                        class3,
                        class5,
                        # eindex,
                        # know_total,
                        homclass,
                        # homclass_s,homclass_w,
                        # prestige,
                        # diversity,
                        pi_nteg,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        Q05pcm,
                        # sstatus,
                        giniwd,
                        ednum,female,agenum,country) %>% na.omit()
dim(dfreg)
dfreg$country <- to_factor(dfreg$country)

sjPlot::plot_model(lmer(redist~1 + female+agenum + homclass*giniwd + pi_nteg+class3 +ednum + Q05pcm + giniwd + (1+homclass|country),data=dfreg),show.values = T)

base <- lmer(redist~1 + (1|country),data=dfreg)
demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
homclass <- lmer(redist~1 + female+agenum + homclass+ (1|country),data=dfreg)
class <- lmer(redist~1 +female+agenum + class3+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + class3+ednum+ Q05pcm + (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + class3 +ednum+homclass + pi_nteg + Q05pcm + (1|country),data=dfreg)
full_int1 <- lmer(redist~1 +female+agenum + homclass*class3+ pi_nteg+ ednum +(1|country),data=dfreg)
full_int3 <- lmer(redist~1 +female+agenum + homclass+pi_nteg*class3+ pi_nteg+ ednum + (1|country),data=dfreg)

models <- list(homclass,class,class_status,full,full_int1,full_int3)
texreg::knitreg(models)
texreg::knitreg(full)
sjPlot::plot_model(full,show.values = T,rm.terms = c("ednum","femaleFemale","agenum")) + geom_hline(yintercept = 0)
ggsave(plot = last_plot(),filename = "model_full.png",device = "png",
       path = here::here("output"),width = 1.5,height = 1,units = "cm",scale = 15)

interplot <- 
interplot::interplot(m = full_int2,var1 = "homclass",var2="class3")

df_int %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  ylab("Class-based homogeneity coefficient")+
  xlab("Social Class")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0)

ggsave(plot = last_plot(),filename = "margins_homoxclass.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)

isolation <- 
interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
df_int2 <- isolation$data
df_int2 <- df_int2[c(1,2,4),]
df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
df_int2
df_int2$value <- factor(df_int2$value,ordered = T,levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

df_int2 %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  ylab("Perceived isolation coefficient")+
  xlab("Social Class")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0)

ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
```

>>>>

Modelos homogeneidad

```{r class-homclass}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot)
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"))
df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (I+II)"
                                           ))
df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (II - lower grade)",
                                           "Service class (I - higher grade)" 
                                           ))
df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
                          as.factor = T,
                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
frq(df1$Q05pcm)
dfreg <- df1 %>% dplyr::select(redist,
                        class6,class3,class5,
                        # tr_inte,
                        # eindex,
                        # know_total,
                        homclass,
                        homclass_s,homclass_w,
                        # prestige,
                        # diversity,
                        # pi_nteg,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        Q05pcm,labst,union,
                        # sstatus,
                        gini_disp,
                        gini_mkt,
                        # palmawd,
                        rgdpna,
                        # giniwb,
                        # giniwd,
                        ednum,female,agenum,country) %>% 
  mutate(logrgdpna=log(rgdpna)) %>% 
  # filter(country!=233) %>% 
  na.omit()

dfreg$homclass_bi <- ifelse(dfreg$homclass>0.5,1,0)
frq(dfreg$homclass_bi)

base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
homclass <- lmer(redist~1 + female+agenum + labst + union+  homclass + (1|country),data=dfreg)
class <- lmer(redist~1 +female+agenum + labst + union+ class3+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + labst + union+ class3+ednum+ Q05pcm + (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass +  Q05pcm + (1|country),data=dfreg)
full_m <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass +  Q05pcm +  gini_disp + logrgdpna + (1|country),data=dfreg)

# Interactions segregation x class
full_int1 <- lmer(redist~1 +female+agenum + homclass*class3+ ednum + Q05pcm + (1|country),data=dfreg)
# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)

models <- list(homclass,class,class_status,full,full_int1)
texreg::knitreg(models)

sjPlot::plot_model(full,show.values = T,rm.terms = c("ednum","femaleFemale","agenum")) + geom_hline(yintercept = 0)
ggsave(plot = last_plot(),filename = "model_full.png",device = "png",
       path = here::here("output"),width = 1.5,height = 1,units = "cm",scale = 15)

# Conditional Marginal effect
interplot <- 
interplot::interplot(m = full_int1,var1 = "homclass",var2="class3")
df_int <- interplot$data
df_int <- df_int[c(1,2,4),]
df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
df_int
df_int$value <- factor(df_int$value,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

df_int %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
  ylab("Class-based homogeneity coefficient")+
  xlab("Social Class")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
  theme(plot.title = element_text(size = 8))

ggsave(plot = last_plot(),filename = "mar_homo_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# Predicted values 
pred1<- plot_model(full_int1,type = "int")
pred_data <- data.frame(pred1$data)
pred_data <- pred_data %>% arrange(pred_data$group)
pred_data$group <- factor(pred_data$group,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

pred_data %>% 
ggplot() +
  geom_point(aes(x = x,y = predicted)) +
  geom_line(aes(x = x,y = predicted))+
  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
  facet_grid(. ~ group) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
  xlab("Network homogeneity")+
  ylab("Redistributive preferences") + 
  theme_minimal()

ggsave(plot = last_plot(),filename = "pred_homo_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# isolation <- 
# interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
# df_int2 <- isolation$data
# df_int2 <- df_int2[c(1,2,4),]
# df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
# df_int2
# df_int2$value <- factor(df_int2$value,ordered = T,
#                         levels = c("Working Class (V+VI+VII)",
#                                    "Intermediate class (III+IV)",
#                                    "Service Class (I+II)"))
# 
# df_int2 %>% 
# ggplot() +
#   geom_point(aes(x = value,y = coef1)) + 
#   geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
#   ylab("Perceived isolation coefficient")+
#   xlab("Social Class")+
#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
#   geom_hline(yintercept = 0)
# 
# ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)

```{r homclass-macro}
# Interactions segregation x inequality
full_int4 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass*gini_disp+ednum + Q05pcm  +logrgdpna + (1+homclass|country),data=dfreg)
# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_nteg*gini_disp+pi_nteg+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)
models_m <- list(full_int4)
texreg::knitreg(models_m)

interplot::interplot(m = full_int4,var1 = "homclass",var2="gini_disp") +
  geom_point()+
  ylab("Class-based homogeneity coefficient")+
  xlab("Economic Inequality")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(full_int4),", Countries=",lme4::ngrps(full_int4))) +  
  theme(plot.title = element_text(size = 8))

ggsave(plot = last_plot(),filename = "mar_homclass_gini.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# interplot::interplot(m = full_int5,var1 = "pi_nteg",var2="gini_disp") +
#   geom_point()+
#   ylab("Perceived isolation coefficient")+
#   xlab("Economic Inequality")+
#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
#   geom_hline(yintercept = 0)
# ggsave(plot = last_plot(),filename = "margins_isolationxgini.png",device = "png",
#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
```

Modelos strong ties

```{r strong-ties}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot)
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"))
df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (I+II)"
                                           ))
df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (II - lower grade)",
                                           "Service class (I - higher grade)" 
                                           ))
df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
                          as.factor = T,
                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
frq(df1$Q05pcm)
dfreg <- df1 %>% dplyr::select(redist,
                        class6,class3,class5,
                        # tr_inte,
                        # eindex,
                        # know_total,
                        homclass,
                        homclass_s,
                        homclass_w,
                        # prestige,
                        # diversity,
                        # pi_nteg,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        Q05pcm,labst,union,
                        # sstatus,
                        gini_disp,
                        gini_mkt,
                        # palmawd,
                        rgdpna,
                        # giniwb,
                        # giniwd,
                        ednum,female,agenum,country) %>% 
  mutate(logrgdpna=log(rgdpna)) %>% 
  # filter(country!=233) %>% 
  na.omit()
dim(dfreg)
base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
homclass <- lmer(redist~1 + female+agenum + labst + union+  homclass_s + (1|country),data=dfreg)
class <- lmer(redist~1 +female+agenum + labst + union+ class3+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + labst + union+ class3+ednum+ Q05pcm + (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass_s + Q05pcm + (1|country),data=dfreg)
full_m <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass_s + Q05pcm + gini_disp + logrgdpna + (1|country),data=dfreg)

# Interactions segregation x class
full_int1 <- lmer(redist~1 +female+agenum + labst + union+ homclass_s*class3+ ednum + Q05pcm + (1|country),data=dfreg)
# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass_s+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)

models <- list(homclass,class,class_status,full,full_m,full_int1)
texreg::knitreg(models)

# Conditional Marginal effect---------------------------------------------------
interplot <- 
interplot::interplot(m = full_int1,var1 = "homclass_s",var2="class3")
df_int <- interplot$data
df_int <- df_int[c(1,2,4),]
df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
df_int
df_int$value <- factor(df_int$value,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

df_int %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  ylab("Class-based homogeneity (s) coefficient")+
  xlab("Social Class")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
  theme(plot.title = element_text(size = 8))

ggsave(plot = last_plot(),filename = "mar_strong-ties_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# Predicted values -------------------------------------------------------------
pred1<- plot_model(full_int1,type = "int")
pred_data <- data.frame(pred1$data)
pred_data <- pred_data %>% arrange(pred_data$group)
pred_data$group <- factor(pred_data$group,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

pred_data %>% 
ggplot() +
  geom_point(aes(x = x,y = predicted)) +
  geom_line(aes(x = x,y = predicted))+
  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
  facet_grid(. ~ group) +
  labs(caption = paste0("N=",nobs(full_int1),", Countries=",lme4::ngrps(full_int1))) +
  xlab("Network homogeneity (strong ties)")+
  ylab("Redistributive preferences") + 
  theme_minimal()

ggsave(plot = last_plot(),filename = "pred_strong-ties_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# isolation <- 
# interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
# df_int2 <- isolation$data
# df_int2 <- df_int2[c(1,2,4),]
# df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
# df_int2
# df_int2$value <- factor(df_int2$value,ordered = T,
#                         levels = c("Working Class (V+VI+VII)",
#                                    "Intermediate class (III+IV)",
#                                    "Service Class (I+II)"))

# df_int2 %>% 
# ggplot() +
#   geom_point(aes(x = value,y = coef1)) + 
#   geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
#   ylab("Perceived isolation coefficient")+
#   xlab("Social Class")+
#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
#   geom_hline(yintercept = 0)

# ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)

```{r strong-ties-macro}
# Interactions segregation x inequality
full_int4 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_s*gini_disp+ednum + Q05pcm +logrgdpna + (1+homclass_s|country),data=dfreg)
# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_s+pi_nteg*gini_disp+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)

models_m <- list(full_int4)
texreg::knitreg(models_m)

interplot::interplot(m = full_int4,var1 = "homclass_s",var2="gini_disp") +
  geom_point()+
  ylab("Class-based homogeneity (s) coefficient")+
  xlab("Economic Inequality")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(full_int4),", Countries=",lme4::ngrps(full_int4))) +  
  theme(plot.title = element_text(size = 8))

ggsave(plot = last_plot(),filename = "mar_strong-ties_gini.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# interplot::interplot(m = full_int5,var1 = "pi_nteg",var2="gini_disp") +
#   geom_point()+
#   ylab("Perceived isolation coefficient")+
#   xlab("Economic Inequality")+
#   ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
#   geom_hline(yintercept = 0)
# 
# ggsave(plot = last_plot(),filename = "margins_isolationxgini.png",device = "png",
#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
```

Modelos weak ties

```{r weak-ties}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot)
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"))
df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (I+II)"
                                           ))
df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (II - lower grade)",
                                           "Service class (I - higher grade)" 
                                           ))
df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
                          as.factor = T,
                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
frq(df1$Q05pcm)
dfreg <- df1 %>% dplyr::select(redist,
                        class6,class3,class5,
                        # tr_inte,
                        # eindex,
                        # know_total,
                        homclass,
                        homclass_s,
                        homclass_w,
                        # prestige,
                        # diversity,
                        # pi_nteg,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        Q05pcm,labst,union,
                        # sstatus,
                        gini_disp,
                        gini_mkt,
                        # palmawd,
                        rgdpna,
                        # giniwb,
                        # giniwd,
                        ednum,female,agenum,country) %>% 
  mutate(logrgdpna=log(rgdpna)) %>% 
  # filter(country!=233) %>% 
  na.omit()
dim(dfreg)
base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
homclass <- lmer(redist~1 + female+agenum + labst + union+  homclass_w + (1|country),data=dfreg)
class <- lmer(redist~1 +female+agenum + labst + union+ class3+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + labst + union+ class3+ednum+ Q05pcm + (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass_w + Q05pcm + (1|country),data=dfreg)
full_m <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+homclass_w + Q05pcm + gini_disp + logrgdpna + (1|country),data=dfreg)

# Interactions segregation x class
full_int1 <- lmer(redist~1 +female+agenum + labst + union+ homclass_w*class3+ ednum + Q05pcm + (1|country),data=dfreg)
# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass_s+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)

models <- list(homclass,class,class_status,full,full_m,full_int1)
texreg::knitreg(models)

# Conditional Marginal effect---------------------------------------------------
interplot <- 
interplot::interplot(m = full_int1,var1 = "homclass_w",var2="class3")
df_int <- interplot$data
df_int <- df_int[c(1,2,4),]
df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
df_int
df_int$value <- factor(df_int$value,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

df_int %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  ylab("Class-based homogeneity (w) coefficient")+
  xlab("Social Class")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
  theme(plot.title = element_text(size = 8))

ggsave(plot = last_plot(),filename = "mar_weak-ties_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# Predicted values -------------------------------------------------------------
pred1<- plot_model(full_int1,type = "int")
pred_data <- data.frame(pred1$data)
pred_data <- pred_data %>% arrange(pred_data$group)
pred_data$group <- factor(pred_data$group,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

pred_data %>% 
ggplot() +
  geom_point(aes(x = x,y = predicted)) +
  geom_line(aes(x = x,y = predicted))+
  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
  facet_grid(. ~ group) +
  labs(caption = paste0("N=",nobs(full_int1),", Countries=",lme4::ngrps(full_int1))) +
  xlab("Network homogeneity (weak ties)")+
  ylab("Redistributive preferences") + 
  theme_minimal()

ggsave(plot = last_plot(),filename = "pred_weak-ties_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)

```{r weak-ties-macro}
# Interactions segregation x inequality
full_int4 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_w*gini_disp+ednum + Q05pcm +logrgdpna + (1+homclass_w|country),data=dfreg)
# full_int5 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass_s+pi_nteg*gini_disp+ednum + Q05pcm + tr_inte +logrgdpna + (1+pi_nteg|country),data=dfreg)

models_m <- list(full_int4)
texreg::knitreg(models_m)

interplot::interplot(m = full_int4,var1 = "homclass_w",var2="gini_disp") +
  geom_point()+
  ylab("Class-based homogeneity (w) coefficient")+
  xlab("Economic Inequality")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(full_int4),", Countries=",lme4::ngrps(full_int4))) +  
  theme(plot.title = element_text(size = 8))

ggsave(plot = last_plot(),filename = "mar_weak-ties_gini.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

# ggsave(plot = last_plot(),filename = "margins_isolationxgini.png",device = "png",
#        path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
```

# Modelos alternativos

@@

### 2023-07-26 procesamiento/prod_prep.Rmd
modelos ok

#frq(df1$v33)
df1$pi_left <- car::recode(df1$v33,recodes = "c(0,8,9)=NA")
df1$pi_left <- set_na(df1$pi_left,na = c(0,8,9))
# df1$pi_left <- sjmisc::rec(x = df1$pi_left,rec = "rev")
sjlabelled::set_label(df1$pi_left) <- "Perceived integration: left out from activities"
#frq(df1$pi_left)
```

@@

```{r}
names(df1)
```

```{r}
save(df1,file = here::here("input/data/proc/study1.RData"))
```

>>>>

#frq(df1$v33)
df1$pi_left <- car::recode(df1$v33,recodes = "c(0,8,9)=NA")
df1$pi_left <- set_na(df1$pi_left,na = c(0,8,9))
# df1$pi_left <- sjmisc::rec(x = df1$pi_left,rec = "rev")
sjlabelled::set_label(df1$pi_left) <- "Perceived integration: left out from activities"
#frq(df1$pi_left)

df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
sjlabelled::set_label(df1$pi_nteg) <- "Perceived integration"
```

# Trust

```{r}
df1$tr_inte <- car::recode(df1$v35,recodes = "c(0,8,9)=NA")
df1$tr_inte <- set_na(df1$tr_inte,na = c(0,8,9))
df1$tr_inte <- sjmisc::rec(x = df1$tr_inte,rec = "rev")
sjlabelled::set_label(df1$tr_inte) <- "Interpersonal trust"
frq(df1$tr_inte)

df1$tr_courts <- car::recode(df1$v36,recodes = "c(98,99)=NA")
df1$tr_courts <- set_na(df1$tr_courts,na = c(98,99))
# df1$tr_courts <- sjmisc::rec(x = df1$tr_courts,rec = "rev")
sjlabelled::set_label(df1$tr_courts) <- "Trust in courts"
frq(df1$tr_courts)
```

@@

# Group-mean center

```{r}

```{r}
df1
save(df1,file = here::here("input/data/proc/study1.RData"))
```
